Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-07 paper.tex
todo
Wording

\texttt{Pipeline} objects are used for chaining multiple estimators into a
single one. This is useful since a machine learning workflow typically involves
a fixed sequence of steps in processing data (e.g., feature extraction,
centering / scaling / normalization, feature selection, learning and making
predictions). For convenience reasons, those steps can be combined into a
pipeline such that \texttt{fit} and \texttt{predict} need to be called only once
to fit the whole sequence. A pipeline also allows for the hyper-parameters of
all the base estimators to be grid-searched all at once. From an API point of
view, a \texttt{Pipeline} object takes as input a sequence of $N$ estimators,
where all $N-1$ first are transformers and the last is either a predictor or a
transformer. Calling \texttt{fit} on the pipeline is the same as calling
\texttt{fit} on each estimator in turn, \texttt{transform} the input and then
pass it on to the next step. The pipeline exposes all the methods the last
estimator in the pipe exposes. That is, if the last estimator is a predictor,
the pipeline can be used itself as a predictor. If the last estimator is a
transformer, then the pipeline is itself a transformer.

@@

As an example, the following snippet illustrates how to create a complex worflow
computing both PCA and Kernel PCA components on \texttt{X\_train} (through a
\texttt{FeatureUninon}), selecting the best of those features and then feeding
them to a linear model:
\begin{verbatim}
Pipeline([("pca", FeatureUnion([('linear_pca', PCA()),
                                ('kernel_pca', KernelPCA())])),
          ("feature_selection", SelectKBest()),
          ("linear_model", LinearRegression())
]).fit(X_train, y_train).predict(X_test)
\end{verbatim}

>>>>

\texttt{Pipeline} objects are used for chaining multiple estimators into a
single one. This is useful since a machine learning workflow typically involves
a fixed sequence of steps in processing data (e.g., feature extraction,
centering / scaling / normalization, feature selection, learning and making
predictions). For convenience reasons, those steps can be combined into a
pipeline such that \texttt{fit} and \texttt{predict} need to be called only once
to fit the whole sequence. A pipeline also allows for the hyper-parameters of
all the base estimators to be grid-searched all at once. From an API point of
view, a \texttt{Pipeline} object takes as input a sequence of $N$ estimators,
where all $N-1$ first are transformers and the last is either a predictor or a
transformer. Calling \texttt{fit} on the pipeline is the same as calling
\texttt{fit} on each estimator in turn, \texttt{transform} the input and then
pass it on to the next step. The pipeline exposes all the methods the last
estimator in the pipe exposes. That is, if the last estimator is a predictor,
the pipeline can be used itself as a predictor. If the last estimator is a
transformer, then the pipeline is itself a transformer. \textcolor{red}{TODO:
Talk about nested attribute syntax.}

@@

As an example, the following snippet illustrates how to create a complex worflow
computing both linear PCA and kernel PCA components on \texttt{X\_train} (through a
\texttt{FeatureUninon}), selecting the best of those features and then feeding
them to a linear model:
\begin{verbatim}
Pipeline([("pca", FeatureUnion([('linear_pca', PCA()),
                                ('kernel_pca', KernelPCA())])),
          ("feature_selection", SelectKBest()),
          ("linear_model", LinearRegression())
]).fit(X_train, y_train).predict(X_test)
\end{verbatim}
